Page not found

### 2023-06-21 manuscript/chapters/4_locality.qmd
finished figures !!! finally

![(TODO the variation for the lower one should be lesser) Intuition behind the average binned variation. To simplify the visualization, activity levels are used in lieu of the 2D positions.](figures/photo_2023-06-15_00-44-43.jpg){width=400px #fig-sketch-binned-variation}

>>>>

![Intuition behind the average binned variation. To simplify the visualization, activity levels are used in lieu of the 2D positions. 4 bins are shown with a different colour. The horizontal line represents the average activity in the bin. From top to bottom: random, column, Z mapping.](figures/fig-variation.svg){width=600px #fig-sketch-binned-variation}
